Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-05 doc/JFLA2022/paper.tex
Update doc/JFLA2022/paper.tex
Co-authored-by: Karl Palmskog <palmskog@gmail.com>

\newcommand{\easychair}{\textsf{easychair}}
\newcommand{\miktex}{MiK{\TeX}}
\newcommand{\texniccenter}{{\TeX}nicCenter}
\newcommand{\makefile}{\texttt{Makefile}}
\newcommand{\latexeditor}{LEd}
\newcommand{\Hydras}{Hydras \& Co.\xspace}
\newcommand{\Coqcommunity}{\emph{Coq-community\xspace} }

@@

\subsection{Vision}
The \Hydras project, part of \Coqcommunity\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \Coqcommunity is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.

>>>>

\newcommand{\easychair}{\textsf{easychair}}
\newcommand{\miktex}{MiK{\TeX}}
\newcommand{\texniccenter}{{\TeX}nicCenter}
\newcommand{\makefile}{\texttt{Makefile}}
\newcommand{\latexeditor}{LEd}
\newcommand{\Hydras}{Hydras \& Co.\xspace}
\newcommand{\Coqcommunity}{Coq-community\xspace}

@@

\subsection{Vision}
The \Hydras project, part of \Coqcommunity~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \Coqcommunity is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
